---
title: "Assignment 1 Report"
author: "Isabeau Lewis"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading libraries
```{r}
library(dplyr)
library(ggplot2)
```

# Loading theme
```{r}
source("http://bit.ly/theme_pub")
theme_set(theme_pub())
```


# Running dataGenerato.R script ??? IS THIS ALL YOU NEED TO DO? I DON'T KNOW IF IT ACTUALLY OUTPUTS

This script creates a simulated data frame with 100 values for four columns: `Organism, Limb_width, Limb_length,` and `Observer` and saves it as a CSV file.
```{r}
source("./dataGenerato.R")
```

# Running volumeEstimato.R script

This script adds an additional `Limb_volume` column calculated from the values for limb width and limb length in the previous script, and saves the file as an updated CSV of the previous one.
```{r echo = TRUE}
source("./volumeEstimato.R")
```

# 1. Loading the revised measurements file
```{r echo = TRUE}
measurements <- read.csv("measurements.csv")
```

# 2. Sorting by column ??? DOES THIS JUST MEAN ARRANGE?
## a) By species
```{r}
arrange(measurements, Organism)
```

## b) By observer
```{r}
arrange(measurements, Observer)
```

## c) By limb volume
```{r}
arrange(measurements, Volume)
```

# 3. Creating a table showing the average volume for each species
```{r}
measurements %>%
  group_by(Organism) %>%
  summarise(avg_Volume = mean(Volume))
```

# 4. Creating a table showing the number of observations for each combination of species and observer
```{r}
measurements %>% 
  group_by(Organism, Observer) %>%
  summarise(Observations = length(c(Organism, Observer)))
```

# 5. Creating a box plot to compare key features of the distributions of volumes for each species ??? DOES THIS NEED A FIGURE CAPTION
```{r}
ggplot(measurements, aes(x=Organism, y=Volume, colour=Organism)) + 
  geom_boxplot() +
  xlab("Species identity") +
  ylab("Limb volume")
```

# 6. Creating a multi-panel plot showing frequency histograms for each species ??? IS THIS WHAT THEY MEAN BY FREQUENCY HIST?
```{r}
ggplot(measurements, aes(x=Volume, group=Organism, fill=Organism, colour=I("black"))) +
  geom_histogram() + # Creating frequency histograms for Volume
  facet_wrap(vars(Organism)) + # Separating frequency histograms by species
  xlab("Limb volume") +
  ylab("Count")

```



